Using SIMD and SIMT vectorization to evaluate sparse chemical kinetic Jacobian matrices and thermochemical source terms

### 2018-06-07 paper.tex
cleanup

SIMD and SIMT programming are two important vector-processing paradigms used increasingly in scientific computing.
Traditional multi-core parallelism \revise{has} often \revise{been} used to increase central processing unit (CPU) performance, \revise{even as the exponential growth in processing power}---colloquially known as Moore's law---has slowed~\cite{khan2018science}.
\revise{Recently, SIMD\slash SIMT processors, e.g., in the form of graphics processing units (GPUs), have gained recognition due to their increased floating operation throughput}.
The parallel programming standard OpenCL~\cite{stone2010opencl} has further enabled adoption of vector processing in scientific computing by providing a common application program interface (API) for execution on heterogeneous systems, e.g., CPU, GPU, or Intel's Many Integrated Core (MIC) architecture.
\revise{Here we will} largely use OpenCL terminology to describe these processing paradigms, as it provides a convenient way to classify otherwise disparate processor types (e.g., CPUs and GPUs).
However, the concepts discussed herein \revise{broadly apply} to SIMD\slash SIMT processing.

>>>>

SIMD and SIMT programming are two important vector-processing paradigms used increasingly in scientific computing.
\revise{Traditional multicore parallelism is now used to increase} central processing unit (CPU) performance, \revise{as the exponential growth in processing power}---colloquially known as Moore's law---has slowed~\cite{khan2018science}.
\revise{Recently, SIMD\slash SIMT processors, e.g., in the form of graphics processing units (GPUs), have gained recognition due to their increased floating operation throughput}.
The parallel programming standard OpenCL~\cite{stone2010opencl} has further enabled adoption of vector processing in scientific computing by providing a common application program interface (API) for execution on heterogeneous systems, e.g., CPU, GPU, or Intel's Many Integrated Core (MIC) architecture.
\revise{Here we will} largely use OpenCL terminology to describe these processing paradigms, as it provides a convenient way to classify otherwise disparate processor types (e.g., CPUs and GPUs).
However, the concepts discussed herein \revise{broadly apply} to SIMD\slash SIMT processing.
